---
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

## Nice job!

We're almost done! We'd just like to ask a few demographic questions which we will only use for analyzing our survey data.

---

## Attention Check

This is an attention check. Please choose Option 1 and continue.

- Option 1
- Option 2

---

## Demographic information

(1) In what year were you born?

(Drop down menu including years `1920` - `2003`)

(2) What is your current gender identity?

Different identity (please state):

- Male
- Female
- Trans male/trans man
- Trans female/trans woman
- Genderqueer/gender non-conforming
- Prefer to self-identify
- Prefer not to say


(3) What is your ethnicity (select all that apply):

Different identity (please state):

- Asian (e.g., Chinese, Filipino, Indian, Vietnamese, Korean, Japanese, Malaysian, etc.)
- African (e.g., African American, Jamaican, Haitian, Nigerian, Ethiopian, Somalian, etc.)
- Caucasian (e.g., German, Irish, English, Italian, Polish, French, etc.)
- Middle Eastern or North African (e.g., Lebanese, Iranian, Egyptian, Syrian, Moroccan, Algerian, etc.)
- Native American or Alaskan Native (e.g., Navajo Nation, Blackfeet Tribe, Mayan, Aztec, Native 
Village of Barrow Inupiat Traditional Government, Nome Eskimo Community, etc.)
- Native Hawaiian or Pacific Islander (e.g., Native Hawaiian, Samoan, Chamorro, Tongan, Fijian, Marshallese, etc.)
- Hispanic or Latino (e.g., Mexican or Mexican American, Puerto Rican, Cuban, Salvadoran, Dominican, Colombian, etc.)


(4) What is your annual household income (from all sources)?

- Less than $10,000
- $10,000 - $19,999
- $20,000 - $29,999
- $30,000 - $39,999
- $40,000 - $49,999
- $50,000 - $74,999
- $75,000 - $99,999
- $100,000 - $149,999
- $150,000 - $199,999
- $200,000 or more
- Prefer not to say


(5) What is your political orientation?

- Strongly conservative
- Conservative
- Leaning conservative
- Moderate
- Leaning liberal
- Liberal
- Strongly liberal
- Independent
- Prefer not to say

(6) What is your primary mode of transportation?

- Personal vehicle
- Public transportation (Bus, Rail, Ferry, etc.)
- Ride-hailing service (e.g. Taxi, Lyft, Uber, Via, UberPool)
- Para-transit services
- Prefer to self-describe

(7) What state do you live in? 

- Alabama
- Alaska
- Arizona
- Arkansas
- California
- Colorado
- Connecticut
- Delaware
- District of Columbia
- Florida
- Georgia
- Hawaii
- Idaho
- IllinoisIndiana
- Iowa
- Kansas
- Kentucky
- Louisiana
- Maine
- Maryland
- Massachusetts
- Michigan
- Minnesota
- Mississippi
- Missouri
- Montana
- Nebraska
- Nevada
- New Hampshire
- New Jersey
- New Mexico
- New York
- North Carolina
- North Dakota
- Ohio
- Oklahoma
- Oregon
- PennsylvaniaRhode Island
- South Carolina
- South Dakota
- Tennessee
- Texas
- Utah
- Vermont
- Virginia
- Washington
- West Virginia
- Wisconsin
- Wyoming


(8) What is the highest degree or level of school you have completed? If currently enrolled, please use the highest degree received.

- Less than a high school diploma
- High school degree or equivalent (e.g. GED)
- Some college or university, no college degree
- Trade/technical/vocational training, no degree awarded
- Associate's degree (e.g. AA, AS)
- Bachelor’s degree (e.g. BA, BS)
- Graduate or Professional Degree (e.g. PhD, MD, JD, MS)
- Prefer not to say

(9) Do you have a religious exemption that prevents you from taking the COVID-19 vaccine?

- Yes
- No

---

Please let us know if you have any other thoughts or feedback on this survey.

Your feedback will help us make future improvements :)

(Open text response)

---

```{r, include=FALSE}
completionCode <- round(runif(1, 10^5, 10^6))
```

### Your completion code is: `r completionCode`

Finish
